Datasheet for Children's Book Ratings

### 2023-03-25 outputs/paper/paper.qmd
Completed Composition section of datasheet

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
```

@@

@@

@@

@@

@@

@@

@@

@@

@@

>>>>

@@

    -   The dataset consists of textual documents. Each row of the overall dataset is a children's book that includes various information about that book.

@@

    -   There are 9241 instances.

@@

    -   The dataset contains a sample of children's books from a larger set of international children's books.

@@

    -   Each instance consists of a ten-digit International Standard Book Number (ISBN), the book title, the author, the number of individuals that gave the book a rating, and the ratings themselves. The "raw" data consists of the features mentioned previously, as well as unadjusted ratings and some metadata, such as cover type and publisher.

@@

    -   No.

@@

    -   Yes, through the unique ten-digit ISBN.

@@

    -   The dataset is linked to a blogpost on Alex Cookson's website, "Rating children's books with empirical Bayes estimation (1 of 2)" [@alexcookson_blogpost]. There are no restrictions associated with the external sour.

@@

    -   No, all data were gathered from public sources.

@@

    -   It is not possible to identify the individuals who have rated the children's books.
